25 Years of Water Quality Change in Rhode Island Lakes and Ponds

### 2018-12-19 manuscript/manuscript.Rmd
some progress on the paper.

>>>>

During the selected sampling period of 1990 to 2016 average lake temperature was `r ww_param_ranges%>%filter(param == "temp")%>%pull(mean)`, average total nitrogen was `r ww_param_ranges%>%filter(param == "total_n")%>%pull(mean)`, average total phosphorus was `r ww_param_ranges%>%filter(param == "total_p")%>%pull(mean)`, and average chlorophyll was `r ww_param_ranges%>%filter(param == "chla")%>%pull(mean)` (`r tab_num("ww_params", display = "cite", caption = "Summary statistics for URI Watershed Watch data from 1990 to 2016.")`)

```{r ww_params, echo=FALSE, results="asis"}
knitr::kable(ww_param_ranges, format = "markdown")
tab_num("ww_params")
```
